Excuse me, do you have a moment to talk about version control?

### 2017-10-05 README.Rmd
Combine sections re: Markdown and Markdown for R users
Remove "holy"

# Markdown is special on GitHub

This may seem unrelated to Git, GitHub, and R, but it is now necessary to talk about [Markdown](https://daringfireball.net/projects/markdown/syntax). Markdown is a markup language, like HTML and LaTeX, but designed to be as lightweight as possible. The goal is still to separate form and content, but also to prioritize human-readability, even at the cost of fancy features. Markdown is in wide use on sites such as [WordPress](https://en.support.wordpress.com/markdown/), [StackOverflow](https://stackoverflow.com/editing-help), and [GitHub](https://help.github.com/categories/writing-on-github/). These sites use Markdown because it allows a diverse population of site users to create decent-looking web content, with hyperlinks and some formatting. Do not build this up into some heroic, LaTeX-level learning task, for it is not. If you can write an email, you can write Markdown.

@@

# Markdown is special for R users

Markdown is especially holy for R users because of [R Markdown](http://rmarkdown.rstudio.com), which is just Markdown that includes chunks of R code.  Figure \ref{fig:report-from-r-or-rmd}A shows a simple `.Rmd` document for our iris example. Again, do not regard R Markdown as something you must clear your schedule to learn. If you can write email and a bit of R code, you can write R Markdown. The [rmarkdown package](https://CRAN.R-project.org/package=rmarkdown) [@rmd-pkg] converts R Markdown (`.Rmd` files) to Markdown (`.md` files), running the code and inserting the results, including figures, into the document. This is powered by another package, [knitr](https://CRAN.R-project.org/package=knitr) [@knitr-pkg; @knitr-book], under the hood. This process is made especially easy in RStudio, but is by no means limited to users of that application. Any R user can call `rmarkdown::render("foo.Rmd")`.

>>>>

# Markdown is special on GitHub and for R users

This may seem unrelated to Git, GitHub, and R, but it is now necessary to talk about [Markdown](https://daringfireball.net/projects/markdown/syntax). Markdown is a markup language, like HTML and LaTeX, but designed to be as lightweight as possible. The goal is still to separate form and content, but also to prioritize human-readability, even at the cost of fancy features. Markdown is in wide use on sites such as [WordPress](https://en.support.wordpress.com/markdown/), [Stack Overflow](https://stackoverflow.com/editing-help), and [GitHub](https://help.github.com/categories/writing-on-github/). These sites use Markdown because it allows a diverse population of site users to create decent-looking web content, with hyperlinks and some formatting. Do not build this up into some heroic, LaTeX-level learning task, for it is not. If you can write an email, you can write Markdown.

@@

Markdown is special for R users because of [R Markdown](http://rmarkdown.rstudio.com), which is just Markdown that includes chunks of R code.  Figure \ref{fig:report-from-r-or-rmd}A shows a simple `.Rmd` document for our iris example. Again, do not regard R Markdown as something you must clear your schedule to learn. If you can write email and a bit of R code, you can write R Markdown. The [rmarkdown package](https://CRAN.R-project.org/package=rmarkdown) [@rmd-pkg] converts R Markdown (`.Rmd` files) to Markdown (`.md` files), running the code and inserting the results, including figures, into the document. This is powered by another package, [knitr](https://CRAN.R-project.org/package=knitr) [@knitr-pkg; @knitr-book], under the hood. This process is made especially easy in RStudio, but is by no means limited to users of that application. Any R user can call `rmarkdown::render("foo.Rmd")`.
